Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-03-01 paper.tex
addition until section 5

This position paper tackles six major problems in computer-aided verification and synthesis for embedded systems, which are (partially) open in current published research.

\textbf{(RP1)} provide suitable encoding into SMT \cite{BarrettSST09}, which may extend the background theories typically supported by SMT solvers, with the goal of reasoning accurately and effectively about realistic embedded programs.

\textbf{(RP2)} exploit SMT techniques to leverage bounded model checking of multi-threaded software, in order to mitigate the state-explosion problem due to thread interleaving.

\textbf{(RP3)} prove correctness and timeliness of embedded systems, by taking into account stringent constraints imposed by hardware.

\textbf{(RP4)} incorporate knowledge about system purpose and associated features, which aims to detect system-level and behavior failures.

\textbf{(RP5)} provide tools and approaches capable of addressing different programming languages and application interfaces, with the goal of reducing the time needed to adapt current verification techniques to new developments and technologies.

\textbf{(RP6)} develop automated synthesis approaches that are algorithmically and numerically sound, in order to handle (control) software that is tightly coupled with the physical environment by considering uncertain models and FWL effects.

\textbf{(RP7)} provide a unified framework, which is able to tackle high and low level properties, as well as system behavior, which can lead to another degree of completeness, in such a way that every implementation aspect of an embedded system is addressed and evaluated.

>>>>

This position paper tackles seven major problems in computer-aided verification and synthesis for embedded systems, which are (partially) open in current published research.

\textbf{(RP1)} provision of suitable encoding into SMT \cite{BarrettSST09}, which may extend the background theories typically supported by SMT solvers, with the goal of reasoning accurately and effectively about realistic embedded programs.

\textbf{(RP2)} exploitation of SMT techniques to leverage bounded model checking of multi-threaded software, in order to mitigate the state-explosion problem due to thread interleaving.

\textbf{(RP3)} proof of correctness and timeliness of embedded systems, by taking into account stringent constraints imposed by hardware.

\textbf{(RP4)} incorporation of knowledge about system purpose and associated features, which aims to detect system-level and behavior failures.

\textbf{(RP5)} provision of tools and approaches capable of addressing different programming languages and application interfaces, with the goal of reducing the time needed to adapt current verification techniques to new developments and technologies.

\textbf{(RP6)} development of automated synthesis approaches that are algorithmically and numerically sound, in order to handle (control) software that is tightly coupled with the physical environment by considering uncertain models and FWL effects.

\textbf{(RP7)} provision of a unified framework, which is able to tackle high and low level properties, as well as system behavior, with the potential to lead to another degree of completeness, in such a way that every implementation aspect of an embedded system is addressed and evaluated.
